Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-11-19 paper/main.tex
shorten Baumann quote

% intro
Results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).
% intro to connectivity and object gradient
[kind of complete overview of (references):] Previous studies suggest that
posterior and anterior part of the PPA show differences in
% connectivity
a) connectivity profiles \citep{baldassano2013differential, baldassano2016two}[+
Nasr et al., 2013; Silson et al., 2016a],
% scenes vs abstract objects
b) a gradient in sensitivity scene and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential},
% low-level scene features
c) differences in response to low-level scene features [Nasr et al., 2014;
Silson et al., 2015; Baldassano et al., 2016a,b; Watson et al., 2016],
% high-level scene features
d) high-level scene features [Park et al., 2014; Aminoff and Tarr, 2015; Linsley
and Macevoy, 2015; Marchette et al., 2015],
% TMS
e) stimulation studies [Rafique et al., 2015] \citep{baldassano2016two}

@@

% baldassano20160two: Neurosynth meta-analysis
\citep{baldassano2016two}'s ``meta-analysis'' using Neurosynth: we compare the
query ``scene'' (47 studies) with the query ``episodic memory, navigation, past
future'' (125 studie).
%
Results: voxels significant only in the scene meta-analysis were concentrated in
the posterior network (66\% in posterior network, 18\% in anterior, 16\% in
other) % baldassano2016two: meta-analysis
\citep{baldassano2016two} Voxels significant in both the scene and
memory/navigation meta-analyses tended to fall near the border between the two
networks and divided approximately equally among them (44\% posterior, 53\%
anterior, 4\% other).
%
\citep{baldassano2016two} Voxels significant only in the memory/navigation
meta-analysis were spread more widely across the cortex, but were concentrated
more in the anterior than the posterior network (16\% posterior, 42\% anterior,
42\% other).

@@

% visuospatial and mnemonic processes
The PHC plays a key role in both visuospatial analysis of scenes [Epstein et
al., 1999, 2003; Park and Chun, 2009; Rajimehr et al., 2011] and (contextual)
mnemonic processing [Aminoff et al., 2013, Bar and Aminoff, 2003; Düzel et al.,
    2003; Janzen and van Turennout, 2004; Baumann et al., 2010; Wegman and
Janzen, 2011] \citep{baumann2016functional}
% associative processing
The PCH has been implicated in the integration and retrieval of contextual
associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
2008a, 2008b].

Contextual associations: relations between objects and conditions that describe,
represent, and bring meaning to an environment [Aminoff et al., 2013]
\citep{baumann2016functional}.
%
Examples: objects that commonly co-occur, such as a refrigerator and an oven
(typically in a kitchen) or familiar spatial configurations of objects, (rows of
tables and chairs in a school classroom). According to this view, activity in
the parahippocampal cortex reflects modality-independent retrieval of contextual
information from memory, such as which objects typically occur in a given scene
and where they are likely to be located relative to one another
\citep{baumann2016functional}.

%
However, it has remained unclear whether these two processes are functionally
and anatomically segregated within the parahippocampal cortex
\citep{baumann2016functional}.
%
We provide evidence for a dissociation between neural activation patterns
associated with visuospatial analysis of scenes and contextual mnemonic
processing along the parahippocampal longitudinal axis
\citep{baumann2016functional}.

%
\citep{baumann2016functional} paradigm: We measure PHC responses while
participants engaged in a task that required them to judge the contextual
relatedness of scene and object pairs, which were presented either as words or
pictures \citep{baumann2016functional}.
%
Participants judged the contextual relatedness of scene and object pairs (“bike”
\& “bell” are a contextually congruent object– object pair, “sofa” \&
“microscope” are incongruent; “boat” \& “lake” are a contextually congruent
object–scene pair, “tractor” \& “hotel” are
incongruent)\citep{baumann2016functional}.
%
Each pair was presented either in printed-word format or in a combined
word–picture format. That allowed us to present pictorial objects and scenes in
isolation (Fig. 1)\citep{baumann2016functional}.
%
To identify visuospatial regions of the PHC, we tested for voxels with greater
activity for picture–scene trials than for picture–object trials over and above
activity differences elicited by the comparison of word–scene trials and word–
object trials\citep{baumann2016functional}.
%
Additionally to locate context-related regions of the PHC, we tested for voxels
that were selectively active during the contextual judgment task regardless of
the type of stimulus (scenes vs objects) or presentation modality (word vs
picture)\citep{baumann2016functional}.

>>>>

% intro
Results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).

% intro to connectivity and object gradient
Kind of complete overview of (references): Previous studies suggest that
posterior and anterior part of the PPA show differences in
% connectivity
a) connectivity profiles \citep{baldassano2013differential, baldassano2016two}[+
Nasr et al., 2013; Silson et al., 2016a],
% scenes vs abstract objects
b) a gradient in sensitivity scene and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential},
% low-level scene features
c) differences in response to low-level scene features [Nasr et al., 2014;
Silson et al., 2015; Baldassano et al., 2016a,b; Watson et al., 2016],
% high-level scene features
d) high-level scene features [Park et al., 2014; Aminoff and Tarr, 2015; Linsley
and Macevoy, 2015; Marchette et al., 2015],
% TMS
e) stimulation studies [Rafique et al., 2015] \citep{baldassano2016two}

@@

% baldassano20160two: Neurosynth meta-analysis
\citep{baldassano2016two}'s ``meta-analysis'' using Neurosynth: we compare the
query ``scene'' (47 studies) with the query ``episodic memory, navigation, past
future'' (125 studie).

%
Results: voxels significant only in the scene meta-analysis were concentrated in
the posterior network (66\% in posterior network, 18\% in anterior, 16\% in
other) % baldassano2016two: meta-analysis
\citep{baldassano2016two} Voxels significant in both the scene and
memory/navigation meta-analyses tended to fall near the border between the two
networks and divided approximately equally among them (44\% posterior, 53\%
anterior, 4\% other).
%
\citep{baldassano2016two} Voxels significant only in the memory/navigation
meta-analysis were spread more widely across the cortex, but were concentrated
more in the anterior than the posterior network (16\% posterior, 42\% anterior,
42\% other).

@@

% visuospatial and mnemonic processes
The PHC plays a key role in
%
a) visuospatial analysis of scenes [Epstein et al., 1999, 2003; Park and Chun,
2009; Rajimehr et al., 2011] and
%
b) (contextual) mnemonic processing [Aminoff et al., 2013, Bar and Aminoff,
2003; Düzel et al., 2003; Janzen and van Turennout, 2004; Baumann et al., 2010;
Wegman and Janzen, 2011] \citep{baumann2016functional}

% associative processing
The PCH has been implicated in the integration and retrieval of contextual
associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
2008a, 2008b]. According to this view, activity in PHC reflects
modality-independent retrieval of contextual information from memory, such as
which objects typically occur in a given scene and where they are likely to be
located relative to one another (contextual associations: relations between
objects and conditions that describe, represent, and bring meaning to an
environment [Aminoff et al., 2013]) \citep{baumann2016functional}.

%
We provide evidence for a dissociation between neural activation patterns
associated with visuospatial analysis of scenes and contextual mnemonic
processing along the parahippocampal longitudinal axis
\citep{baumann2016functional}.

%
Paradigm: Participants had to judge the contextual relatedness of scene and
object pairs (presented either as words or pictures)
\citep{baumann2016functional}.
%
Participants judged the contextual relatedness of scene and object pairs (“bike”
\& “bell” are a contextually congruent object– object pair, “sofa” \&
“microscope” are incongruent; “boat” \& “lake” are a contextually congruent
object–scene pair, “tractor” \& “hotel” are
incongruent)\citep{baumann2016functional}.
%
Each pair was presented either in printed-word format or in a combined
word–picture format. That allowed us to present pictorial objects and scenes in
isolation (Fig. 1)\citep{baumann2016functional}.

%
1) To identify visuospatial regions of the PHC, we tested for voxels with
greater activity for picture–scene trials than for picture–object trials over
and above activity differences elicited by the comparison of word–scene trials
and word– object trials\citep{baumann2016functional}.
%
2) To locate context-related regions of the PHC, we tested for voxels that were
selectively active during the contextual judgment task regardless of the type of
stimulus (scenes vs objects) or presentation modality (word vs
picture)\citep{baumann2016functional}.
